
\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Rutvik Joshi} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{ Halifax, CA} 
\address{{\href{mailto:rutvikjoshi.tech@gmail.com}{RutvikJoshi.tech@gmail.com} \\ \href{https://linkedin.com/in/rutvikjoshi}{linkedin.com/in/RutvikJoshi} \\
\href{https://github.com/RutvikJ77}{github.com/RutvikJ77}} \\ \href{https://rutvikjoshi.me}{rutvikjoshi.me}}

\begin{document}
%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

% \begin{rSection}{OBJECTIVE}

% {Analysis}


% \end{rSection}

%----------------------------------------------------------------------------------------
% Skill Summary	
%----------------------------------------------------------------------------------------
% \begin{rSection}{ABOUT}
% I am a creative and logical problem solver leveraging the potential of data and empathy for providing insights and services to users complying with agile practices of growth. I value community diversity, growth and Open-source.


% \end{rSection}




%----------------------------------------------------------------------------------------
% TECHNICAL STRENGTHS	
%----------------------------------------------------------------------------------------
% \begin{rSection}{SKILLS}

% \begin{tabular}{ @{} >{\bfseries}l @{\hspace{2ex}} l }
% Soft Skills & Management, Creativity, Research, Storytelling, Teamwork\\
% Developer Tools & VS Code, Tableau, Microsoft Office, Google suite, Git, Notion\\
% Languages \& Databases & Python, R, SQL, PostgreSQL, MySQL, MongoDB\\
% Libraries \& Platforms & Tensorflow, Numpy, Pandas, Sci-kit learn, Seaborn, Matplotlib, GCP, Heroku\\


% \end{tabular}
% \end{rSection}

\begin{rSection}{SKILLS} 
Business Analysis, Process Development, Strategic Planning, Data Analysis, Communication, Problem-solving, SQL, Relational Databases, Project Management Tools(Jira, Confluence), Tableau, Python, DeepLearning, Blockchain
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}

\textbf{IT Developer} \hfill September 2023 - Ongoing\\
Canada Revenue Agency \hfill \textit{Canada, Remote}
 \begin{itemize}
    \itemsep -3pt {} 
    \item Analyzed business requirements for 12+ internal applications, coordinating with 14 team leads to document effort estimates. Developed new estimation templates, improving change estimation calculation.
    \item Optimized release scheduling and workload distribution view by developing 3 Jira dashboards using JQL, enhancing team efficiency. Conducted 50+ change management assessments with an average resolution of 3 days.
    \item Managed and monitored 65+ conversations for the Project Office of T3 tax file system, ensuring active resolution to inquiries and issues. Revising and suggesting impactful approaches to the supervisor for following up with 16 team leads and 6 cross-functional managers. 
    \item Created 20+ Jira filters and 4 dashboards, saving the team 100 minutes daily and improving the visibility of urgent items. Automated critical reports in Excel for the sectional director, reducing report generation time by 40\% and enhancing data accuracy.
 \end{itemize}

% \textbf{IT Analyst (Co-op)} \hfill September 2023 - December 2023\\
% Canada Revenue Agency \hfill \textit{Canada, Remote}
%  \begin{itemize}
%     \itemsep -3pt {} 
%     \item Managed and monitored 65+ folders of the Project Office mailbox for T3 Modernization, ensuring active resolution to inquiries and issues. Revising and suggesting impactful approaches to the team lead for following up with 16 team leads and 6 cross-functional managers. 
%     \item Created 20+ Jira filters and 4 dashboards, saving the team 100 minutes daily and improving visibility of urgent items. Automated critical reports in Excel, reducing report generation time by 40\% and enhancing data accuracy.


%  \end{itemize}

\textbf{Vessel Data Analyst} \hfill May 2023 - August 2023\\
Rimot.io(BlueGrid) \hfill \textit{Canada, Halifax}
 \begin{itemize}
    \itemsep -3pt {} 
    \item Analyzed energy consumption patterns of 3 lobster fishing vessels, achieving 94\% correlation between cumulative energy and time, by processing and visualizing real-time data from CANEdge devices.
    \item Developed Grafana dashboards to evaluate vessel trips, resulting in the identification of data anomalies and discrepancies, through querying AWS Timestream using TSQL and creating visualizations for KPIs. Presented data-driven recommendations to management, influencing strategic decisions on fleet modernization.
    \item Optimized power-speed relationship analysis, achieving improved R2 values, by implementing various curve fitting methods including linear, cubic, and sigmoid fits. Conducted hypothesis testing in Python, achieving an 89\% success rate in predicting vessel electrification.
 \end{itemize}


\textbf{Ecosystem Marketing Manager \& Analyst} \hfill October 2021 - February 2023\\
Polygon Labs \hfill \textit{USA, Remote}
 \begin{itemize}
    \itemsep -3pt {} 
    \item Advising and consulting 45+ Blockchain Web3 projects with GTM strategies including the frameworks, and processes for the long-term sustenance of the projects. Partnering with 6 cross-functional global social engagement teams, and delivering high-impact presentations to senior executives.
    \item Synthesised multiple endpoints from internal and community-based narratives to script the monthly developer and institutional newsletter, bringing 5K+ and 900 readers with 23\% open rates over a month.
    \item Developed a Python web application for user insights and analyzed DeFi projects using SQL, driving a 35\% improvement in campaign effectiveness.
    \item Generated data-driven market research reports, leading to a 270\% increase in social media engagement across multiple channels. Reported the insights to the CMO raising a propelling shift to the marketing strategy.

 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{0.05em}

\href{https://github.com/RutvikJ77/Resume-aid}{\textbf{\underline{Resume-Aid}}} $|$\textit{ Python, Streamlit, Spacy, Numpy, Pandas}
\begin{itemize}
    \item Simplified ATS compatibility checks by developing a resume evaluation tool using SpaCy, Scikit-learn, and cosine similarity, enabling users to optimize resumes for job descriptions.
    \item Processed resumes with doc2text and Rake NLTK to extract and score key phrases, improving applicant visibility in recruitment pipelines by up to 30\%.
    % \item  {Analyzed Resumes to provide accurate insights and scores using RAKE and cosine similarity for particular words that co-relate with the presented job description.}
    % \item{Gather a list of \textbf{top 10} phrases and words from your resume and generate a top 20 importance and similarity list to calculate the final score and display it through a web application.}
\end{itemize}

\href{https://github.com/RutvikJ77/ExAncient}{\textbf{\underline{ExAncient}}} $|$\textit{ Python, Flask, Tensorflow, SciKit-Learn}
\begin{itemize}
    \item {Imparted an experience of ancient style paintings with modern user input photographs using Image Style Transfer deep learning technique.}
    \item {Generate a romantic story based on the Photograph using a Convolutional Neural Network and a caption model generator with 95\% accuracy.}
\end{itemize}

\href{https://github.com/RutvikJ77/FoodNCulture}{\textbf{\underline{FoodNCulture}}} $|$\textit{ Java, Android, Figma, SOLID}
\begin{itemize}
  \item Conceptualized and implemented a community-driven web platform using Java and MySQL, fostering cultural exchange by connecting hosts and guests through food-sharing events.
  \item Designed a robust backend architecture with modules for user authentication, payments, event management, and chat, ensuring seamless and secure user interactions.
  \item Enhanced user engagement through an interactive community forum and donation system, promoting inclusivity and sustainability within immigrant and student communities.
\end{itemize}

% \href{https://github.com/RutvikJ77/Smart-queue-management}{\textbf{\underline{Smart Queue Management}}} $|$\textit{ Jupyter Notebook, Intel OpenVino toolkit, Tensorflow}
% \begin{itemize}
%     \item  {Determines if a shop queue has reached its maximum number from input video footage using custom-built person detection algorithm and OpenCV.}
%     \item {Generates a warning in real time using Intel openvino edge computing toolkit if the queue exceeds the maximum count.}
% \end{itemize}

% \href{https://github.com/RutvikJ77/RetStock}{\textbf{\underline{RetStock}}} $|$\textit{ Python, Streamlit, Matplotlib}
% \begin{itemize}
% \item Developed a data visualization platform using Streamlit, Yahoo Finance API, and Tweepy to analyze stock trends influenced by social media sentiment.
% \item Integrated Natural Language Toolkit (NLTK) for sentiment analysis of Twitter data, correlating tweet volume and sentiment with stock price movements over time.
% \item Enabled informed decision-making for retail investors by graphically overlaying real-time tweet metrics and financial market data, enhancing trend insights.
% \end{itemize}

\href{https://github.com/RutvikJ77/Inspiquote}{\textbf{\underline{Inspiquote}}} $|$\textit{Python, Rest API, Numpy, Pandas}
\begin{itemize}
  \item Created a daily motivational Twitter bot using Tweepy, Unsplash API, and Pillow, combining quotes with curated images, resulting in an engaging visual experience for users.
  \item Automated content generation with Rapid Automatic Keyword Extraction (Rake-NLTK) and scheduled posts via APScheduler, enhancing user interaction through timely motivational tweets and replies.
  \item Deployed on Heroku, ensuring scalable operations and consistent user engagement, including personalized direct messages and retweets every 8 hours.
\end{itemize}

\href{https://github.com/RutvikJ77/Case-Predictor}
{\textbf{\underline{Case-Predictor}}} $|$\textit{ Python, Jupyter Notebook, Streamlit, SciKit-Learn, matplotlib}
\begin{itemize}
  \item Engineered a machine learning library(infectpredict) leveraging ensemble models like LSTM, GRU, CNN, and meta-features to enhance prediction accuracy, achieving a Mean Squared Error (MSE) of 3575.
  \item {Designed and deployed Case Predictor, an interactive Streamlit app powered by TensorFlow and Scikit-Learn, enabling real-time infection rate predictions.}
  \item {Applied advanced feature engineering and 3-fold cross-validation to optimize data preprocessing and modeling pipelines, improving convergence and reducing error rates.}
\end{itemize}

% \href{https://public.tableau.com/app/profile/rutvik.j/viz/ImportExportAnalysis/ImportExportAnalysis}{\textbf{\underline{Population of world on Internet}}} $|$\textit{ Python, Tableau, MS-Excel}
% \begin{itemize}
%     \item Developed a comprehensive Tableau visualization to analyze import and export commodity data for India pre-pandemic, allowing stakeholders to quickly identify trends and opportunities for growth.
%     \item {Conducted data analysis on trade data from various sources, including government agencies and industry associations using Python, to ensure accuracy and relevance of the Tableau visualization for the stakeholders.}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Master of Applied Computer Science \hfill {}}\\
\textit{Dalhousie University} \hfill{\textit{Halifax, CA}}

{\bf Bachelor of Engineering in Computer Engineering \hfill {}}\\
\textit{University of Mumbai(CGPA - 9.03/10)} \hfill{\textit{Mumbai, IN}}


\end{rSection}




%----------------------------------------------------------------------------------------
% \begin{rSection}{Certifications \& Specializations} 
% Deep Learning(Deeplearning.ai), Intel Edge AI developer Nanodegree(Udacity), 
% Google Data Analytics(Coursera), Blockchain Specialization(Coursera),
% Business Intelligence and Data Analytics(Coursera)
% \end{rSection}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
\begin{rSection}{Achievements and Extra-Curricular Activities} 
\begin{itemize}
    \item \textbf{Awarded Best Hack} and \textbf{Best International Team} at Kent Hack Enough Hackathon 2020.
    \item Won the Saint Mary University's 1st Innovation Cup challenge among 17 teams. Awarded as the \textbf{best team lead} and winning team for York University's Business Analytics course with IBM.
    % \item Ranked in \textbf{Top 20\%} at \textbf{Qiskit Quantum India Challenge}.
    \item Mentored at Canada's biggest hackathon \textbf{Hack The North} and at North Texas's largest Hackathon \textbf{HackUTD}VII Seas. Led a team of 4 at 15+ international hackathons.
    \item \textbf{Guest Speaker} at Atlantic Canada’s startup incubator Shiftkey Labs for Introduction to Blockchain.
    \item Won \textbf{Best Data Science} project at TheGoldenHack 2021 and overall \textbf{First} from 130+ projects at MLH DataDayGrind 2.0. 
    % \item Led a team of 4 at over 15+ international hackathons.
    % \item Selected from a pool of 10000+ applicants to learn about the upcoming AI change of Edge computing for \textbf{Intel Edge AI scholarship}.
    % \item Selected as \textbf{SkillShare Scholarship} recipient from a pool of candidates to learn about diverse courses available from distinct instructors.
    % \item Collaborated and guided a group of \textbf{12 CyberSecurity} enthusiasts to visit Imedita in Pune.
    % \item Volunteered and promoted the agenda of \textbf{RIO+25} program organized by \textbf{United Nations Sustainable Development group} to 45 students.
    % \item \textbf{Head Organizer} and a guide for 126 students for an Industrial visit to Kitec, Silvassa about 188KM away from home destination.
\end{itemize}
\end{rSection}


\end{document}
